\section{Experience}
	\begin{itemize}[noitemsep, left=0pt, labelsep = 0pt]
		\item[\linkedlist{Work Experience 1}] { % use \linkedlist{label} to link this item to the next one
			\begin{Experience} % use the Experience environment to create a new experience using especial formatting
				{\textbf{IT Analyst}, BTG Pactual, São Paulo, SP, Brazil}
				{04/2022 - 06/2024}
			\end{Experience} 
			 
			\begin{highlights}
				\item Led the development of a Full-Stack system (C\#, React, MySQL, SQL Server, and RabbitMQ) for report management, ensuring contractual compliance and mitigating financial risks associated with integrating a new fund manager to the company's portfolio.
				\item Led the modernization of the reporting system, transitioning from SQL procedures to a microservices architecture, resulting in a 50\% reduction in execution time and enabling parallel report generation.
				\item Modernized legacy systems using microservices (C\#, MySQL, RabbitMQ), improving system scalability and operational efficiency of fund calculation systems by 40\%, while also enabling automated processes.
				\item Developed and executed unit and integration tests, ensuring continuous quality through CI/CD pipeline integration, and achieved 100\% code coverage for the domain logic.
				\item Analyzed system performance using Datadog to optimize cost efficiency while balancing availability and scalability, leading to a 30\% reduction in system costs.
				\item Collaborated with business teams to maintain and enhance VB- and SQL-based systems, ensuring service quality and avoiding rework for the business teams.
				\item Managed Excel macros and SQL queries for 60\% of offshore capital flow, ensuring efficiency and accuracy.
			\end{highlights} 
		}
		
		\item[\linkedlist{Work Experience 2}] {
			\begin{Experience}
				{\textbf{IT Intern}, BTG Pactual, São Paulo, SP, Brazil}
				{05/2021 - 04/2022}
			\end{Experience}
			
			\begin{highlights}
					\item Implemented improvements in Excel macros and Access/MySQL databases, optimizing processing times by 60\%.
					\item Initiated the development and implementation of unit tests in C\#, contributing to service quality.
					\item Developed automation scripts to handle code changes, reducing the time spent on simple link update tasks by 80\%.
			\end{highlights}
		}

		\item[\linkedlist{Work Experience 3}] {
			\begin{Experience}
				{\textbf{Automation Intern}, BTG Pactual, São Paulo, SP, Brazil}
				{01/2021 - 05/2021}
			\end{Experience}
			
			\begin{highlights}
					\item Developed RPA automations, reducing the execution time of repetitive tasks by 25 hours daily.
					\item Created a Teams bot for web scraping and automated news delivery, optimizing communication and reducing the time spent searching for relevant information.
			\end{highlights}
		}
	\end{itemize}

	% draw line between the items, need to add a new draw line for each new item
	\vspace{-\baselineskip}
	\begin{tikzpicture}[remember picture, overlay]
		\draw[gray] (Work Experience 1) -- (Work Experience 2);
		\draw[gray] (Work Experience 2) -- (Work Experience 3);
	\end{tikzpicture}
	\vspace{-\baselineskip}